### 2016-01-26 project/paper/appendices/productivity.tex
fixed appendices

\section{Discussion on work productivity}

@@

The assignment was to find a research question revolving around the knowledge base, enriched with information from other sources. Because we found an interesting knowledge base on Nobel Prizes, the posed research question wasn't a far fetch. The problem is that in order to build a model on who would win a Nobel Prize, we need positive and negative examples. The positive examples are the Nobel laureates, which come from a pool of scientists. All other scientists naturally serve as negative examples. Since a politician isn't eligible to receive such prize, we can't use them as negative examples. It is thus inevitable to use different examples in the training set and the testing set.

@@

\subsubsection{Work productivity duality}
An interesting duality exists in both measures. Having a lot of publications over a mediocre amount can be recognised by the model as either a \emph{good} or \emph{bad} property. It can for example mean that someone is just trying to publish a lot of less significant results, while a mediocre amount of significant results might be more important. For speeches the same happens, where a lot of speeches might just as well mean that a politician is only talking, without actually \emph{doing} much. This re\"inforces our belief that both might be a good proxy for the same feature.

>>>>

\section{Discussion on work productivity}
\label{sec:productivity}

@@

The assignment was to find a research question revolving around the knowledge base, enriched with information from other sources. Because we found an interesting knowledge base on Nobel Prizes, the posed research question wasn't a far fetch. The problem is that in order to build a model on who would win a Nobel Prize, we need positive and negative examples. The positive examples are the Nobel laureates, which come from a pool of scientists. All other scientists naturally serve as negative examples. Since a politician isn't eligible to receive such prize, we can't use them as negative examples. It is thus inevitable to use different examples in the training dataset and the research dataset.

@@

\subsubsection{Work productivity duality}
An interesting duality exists in both measures. Having a lot of publications over a mediocre amount can be recognised by the model as either a \emph{good} or \emph{bad} property. It can for example mean that someone is just trying to publish a lot of less significant results, while a mediocre amount of significant results might be more important. For speeches the same happens, where a lot of speeches might just as well mean that a politician is only talking, without actually \emph{doing} much. This reinforces our belief that both might be a good proxy for the same feature.

### 2016-01-26 project/paper/sections/methodology.tex

\section{Methodology}
\label{sec:methodology}
To answer the research question we will use the approach described below. The next sections will explain the steps more thoroughly.
\begin{enumerate}
\item We think about what properties of previous Nobel Prize winners might be interesting to incorporate in learning a model. This is the feature selection step. Furthermore, we determine whether and where this information can be found.
\item The available data is then collected by the aid of SPARQL queries and scraping webpages. This is combined into a training dataset and a research dataset. The training dataset consist of all features for scientists and economists that have or have not won a Nobel Prize. This can be used to learn a predictive model. The research data set contains the same features, but then for politicians for which we would like to answer the research question.
\item Some statistics are applied to the training data to assess its quality. For example, because collecting the data is prone to errors, some outlier detection and removal has to be perfomed.
\item The final training dataset is used to learn a model that is able to predict how likely a person is to win a Nobel Prize. A logistic regression model is used. Because it predicts the probability of particular outcomes, it is perfectly suited to answer the research question. The model's accuracy is assessed using cross-validation on the training dataset.
\item The final step is applying the learned model on the training dataset and discussing its results. 
\end{enumerate}

>>>>

\section{Methodology}
\label{sec:methodology}
To answer the research question we will use the approach described below. The next sections will explain the steps more thoroughly.
\begin{enumerate}
\item We think about what properties of previous Nobel Prize winners might be interesting to incorporate in learning a model. This is the feature selection step. Furthermore, we determine whether and where this information can be found.
\item The available data is then collected by the aid of SPARQL queries and scraping webpages. This is combined into a training dataset and a research dataset. The training dataset consist of all features for scientists and economists that have or have not won a Nobel Prize. This can be used to learn a predictive model. The research dataset contains the same features, but then for politicians for which we would like to answer the research question.
\item Some statistics are applied to the training data to assess its quality. For example, because collecting the data is prone to errors, some outlier detection and removal has to be performed.
\item The final training dataset is used to learn a model that is able to predict how likely a person is to win a Nobel Prize. A logistic regression model is used. Because it predicts the probability of particular outcomes, it is perfectly suited to answer the research question. The model's accuracy is assessed using cross-validation on the training dataset.
\item The final step is applying the learned model on the research dataset and discussing the results. 
\end{enumerate}
